refractory erectile dysfunction (by ArticleAggregator_v05)

### 2023-02-22 ArticleAggregatorCS.qmd
eb_src.xlsx uploaded to AAdata-Refr_ED

---
title: "ramipril cough amlodipine (by ArticleAggregator_v05)"
author: "ReCodeRa"
format: html
server: shiny
editor: 
  markdown: 
    wrap: 72
---

@@

```{r}
#| label: Environment Setup
final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT", "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
term <- "ramipril cough amlodipine"
aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/rami/"
setwd(aa_path)
```

>>>>

---
title: "refractory erectile dysfunction (by ArticleAggregator_v05)"
author: "ReCodeRa"
format: html
server: shiny
editor: 
  markdown: 
    wrap: 72
---

@@

```{r}
#| label: Environment Setup
final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT", "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
term <- "refractory erectile dysfunction"
aa_path <- "/workspaces/WebScrap/ArticleAggregator_data/refrac_ED/"
setwd(aa_path)
```
